### 2016-02-05 docs/ms_communitySynchrony.Rmd
trying new intro

<!-- \setlength{\parindent}{5ex} -->
\setlength{\parindent}{5ex}

Introduction
------------
Asynchrony in population dynamics (also called compensatory dynamics) among interacting species is a key mechanism by which biodiversity can stabilize aggregate community or ecosystem function [@Ives2002; @Gonzalez2009; @Loreau2010; @Loreau2013].
Experimental work in grassland communities provides strong evidence for the stabilizing effect of asynchronous population dynamics [@Hector2010; @DeMazancourt2013a; @Gross2014; @Hautier2014], but identifying what drives species synchrony in natural communities remains a challenge [@Loreau2008a; @Gonzalez2009; @Loreau2013].
The challenge lies in partitioning community synchrony among three mechanistic drivers of population fluctuations: inter and intraspecific density-dependence, environmental stochasticity, and demographic stochastcity [@Loreau2008a].
Ideally, each mechanism would produce a unique signature on community dynamics and we could infer mechanism by comparing observed synchrony to some null expectation [e.g., @Houlahan2007].
Unfortunately, theoretical work suggests there is no null expectation of community synchrony and the drivers of synchrony interact in complex ways that preclude inference from observations alone [@Loreau2008a; @Loreau2013].

@@

<!-- COMMENT THIS OUT FOR NOW...
Futhermore, analyses of observational time series tend to report synchronous, rather than asynchronous, population dynamics among species of similar ecology [@Houlahan2007; @Mutshinda2009; @Rocha2011; @Vasseur2014].
Thus, our understanding of the prevalence and drivers of asynchronous population dynamics is limited.
Only by fully understanding the mechanisms that lead to asynchronous, or synchronous, dynamics in natural ecosystems can we predict how future biodiversity loss may impact ecosystem functioning [@Loreau2010].

@@

In this paper, we seek to overcome the limitations of previous studies by explicitly testing theory on all the drivers of species synchrony using empirically-based, multi-species population models that include the effects of density-dependence, environmental stochasticity, and demographic stochasticity.
We follow the theory of @Loreau2008a, who show that in a neutral community of *S* species, expected synchrony ($\phi_r$) is defined as:

>>>>

\newpage{}
<!-- THIS HOW TO COMMENT-OUT -->
\setlength{\parindent}{5ex}

Introduction
------------
The temporal synchrony of population dynamics among interacting species largely determines ecosystem stability [@Ives2002; @Loreau2013; @Gross2014] and is a function of demographic stochasticity, environmental stochasticity, and competition [@Loreau2008a; @Loreau2013].
Strong asynchrony (also called compensatory dynamics) can emerge from negative interactions among competitors [@Lehman2000], but can also be the result of species-specific responses to environmental conditions [@Loreau2013].
However, it may often be the case that communities are composed of species that respond similarly to environmental conditions, which can synchronize community dynamics [@Houlahan2007; @Rocha2011].
Competition, too, may synchronize dynamics under some conditions [@Loreau2013].
In fact, demographic stochasticity is the only force with a consistent desynchronizing effect on population dynamics [@Loreau2008a].
Since environmental forces and competition can both lead to strong synchronous or asynchronous dynamics, deciphering the mechanisms behind species synchrony in natural communities has been a challenge.

One of the largest hurdles to understanding community synchrony has been how we define synchrony.
Unfortunately, the null expectation of independent species fluctutations and the use of summed community covariance as a metric of synchrony resulted in the perception that synchrony and asynchrony are binary states [@Ives1995; @Klug2000; @Fischer2001; @Houlahan2007], when in fact synchrony is a continuous property [@Loreau2008a].
Fortunately, two recent theoretical advances clarify how we should view community syhnchrony.
First, there is no null expectation of community synchrony.
Theory identifies several limiting cases, but none can be considered null expectations [@Loreau2008a; @Loreau2013].
For example, independent fluctuations among species is one expected theoretical outcome, but only when demographic stochasticity alone is operating and all species have equal abundances and variances [@Loreau2008a].
Another expectation is that species fluctuate in perfect synchrony when competition and demographic stochasticity are weak and species' responses to the environment are perfectly correlated [@Loreau2008a].
It is impossible to *a priori* assign a theoretical expectation to a natural community, suggesting we should abandon the use of any null expectation.
Second, @Loreau2008a derived a new metric of synchrony ($\phi$) from a multi-species dynamic population model, which makes clear that synchrony and asynchrony are not binary states, contrary to their common usage in the literature.
Rather, the synchrony of community dynamics lies along a continuum from perfect asynchrony ($\phi=0$) to perfect synchrony ($\phi=1$).
Thus, our focus should not be on whether or not (a)synchronous dynamics occur, but instead on the degree of (a)synchrony within a community and what process increase or decrease sychrony [e.g., @Gross2014].

Since there is no null expectation for synchrony, no breakpoint at which dynamics can be considered asynchronous or synchronous, and values of synchrony are not unique to specific processes, it is impossible to infer the relative strength of different mechanisms driving synchrony by calculating summed covariances of population time series [e.g., @Houlahan2007].
To overcome the limitations of analyzing community covariance alone, @Mutshinda2009 used a statistical approach to decompose fluctuations in abundance into contributions from environmental stochasticity and species' interactions.
In agreement with Houlahan et al.'s (2007) conclusions, @Mutshinda2009 found that community dynamics were driven by positively correlated environmental responses among species.
However, the @Mutshinda2009 study did not include data from plant communities that have, so far, received the most evidence for a strong role for interspecific interactions in determining species synchrony [@Gross2014].

In this paper, we explicitly test theory on all the drivers of species synchrony by parameterizing and simulating dynamic multi-species population models fit to long term demographic data from five semi-arid grasslands [@Chu2015].
We make no *a priori* assumptions about expected synchrony or the potential for drivers of population dynamics to increase or decrease synchrony.
Instead, we use the fitted population models to simulate communities with and without interspecific interactions, environmental forcing, and demographic stochasticity.
Our modeling approach allows us to draw inference from real ecological systems that would otherwise be impossible using strictly statistical [e.g., @Mutshinda2009], experimental [e.g., @Gross2014], or observational [e.g., @Houlahan2007] approaches.
Given that our models capture the essential features of community dynamics important to synchrony (density-dependence, demographic and environmental stochasticity) and that these models are able to reproduce observed plant abundances [@Chu2015], perturbing the models reveals the processes responsible for the degree of species synchrony in our focal grassland communities.

<!-- COMMENT THIS OUT FOR NOW...

We follow the theory of @Loreau2008a, who show that in a neutral community of *S* species, expected synchrony ($\phi_r$) is defined as:

Asynchrony in population dynamics (also called compensatory dynamics) among interacting species is a key mechanism by which biodiversity can stabilize aggregate community or ecosystem function [@Ives2002; @Gonzalez2009; @Loreau2010; @Loreau2013].
Experimental work in grassland communities provides strong evidence for the stabilizing effect of asynchronous population dynamics [@Hector2010; @DeMazancourt2013a; @Gross2014; @Hautier2014], but identifying what drives species synchrony in natural communities remains a challenge [@Loreau2008a; @Gonzalez2009; @Loreau2013].
The challenge lies in partitioning community synchrony among three mechanistic drivers of population fluctuations: inter and intraspecific density-dependence, environmental stochasticity, and demographic stochastcity [@Loreau2008a].
Ideally, each mechanism would produce a unique signature on community dynamics and we could infer mechanism by comparing observed synchrony to some null expectation [e.g., @Houlahan2007].
Unfortunately, theoretical work suggests there is no null expectation of community synchrony and the drivers of synchrony interact in complex ways that preclude inference from observations alone [@Loreau2008a; @Loreau2013].

@@

Futhermore, analyses of observational time series tend to report synchronous, rather than asynchronous, population dynamics among species of similar ecology [@Houlahan2007; @Mutshinda2009; @Rocha2011; @Vasseur2014].
Thus, our understanding of the prevalence and drivers of asynchronous population dynamics is limited.
Only by fully understanding the mechanisms that lead to asynchronous, or synchronous, dynamics in natural ecosystems can we predict how future biodiversity loss may impact ecosystem functioning [@Loreau2010].

@@
